---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(here)
```

# eurobarometer

<!-- badges: start -->
[![dataobservatory on Github](https://img.shields.io/badge/github-dataobservatory.eu-6e5494.svg)](https://github.com/dataobservatory-eu/)
[![R package retroharmonize](https://img.shields.io/badge/R-retroharmonize-007CBB.svg)](https://retroharmonize.dataobservatory.eu)
[![dataset](https://img.shields.io/badge/R-dataset-E4007F.svg)](https://dataset.dataobservatory.eu)
[![Contributor Covenant](https://img.shields.io/badge/ethics-Contributor%20Covenant-680171.svg)](https://dataobservatory.eu/)
[![Project Status: Active. The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/dataobservatory-eu/eurobarometer?branch=main&svg=true)](https://ci.appveyor.com/project/dataobservatory-eu/eurobarometer)
<!-- badges: end -->

The goal of eurobarometer is to provide helper functions for the use of the [retroharmonize](https://retroharmonize.dataobservatory.eu/) package when working with SPSS versions of the Eurobarometer surveys files that are stored at GESIS. This package was not made, and is not affiliated with GESIS.

Currently `eurobarometer` can be seen as a development version of the [retroharmonize](https://retroharmonize.dataobservatory.eu/) pacakge. Some important functions of retroharmonized are being modernized with new dependencies: a new questionbank, [DDIwR](https://eurobarometer.dataobservatory.eu/articles/dependencies.html), [dataset](https://dataset.dataobservatory.eu/) and [declared](https://declared.dataobservatory.eu/). After thorough testing, most of these functions will be moved back to _retroharmonize_.  Eurobarometer will remain a helper package to use _retroharmonize_ with Eurobarometer surveys. It will serve as a template for similar works with other survey programs, for example, _Afrobarometer_. 


## Overview

- [Articles](https://eurobarometer.dataobservatory.eu/articles/index.html) on the package website.
- [Function reference](https://eurobarometer.dataobservatory.eu/docs/reference/index.html).

## Installation

Because `eurobarometer` is in an early development phase, you cannot install it from CRAN with the `install.packages("eurobarometer")` command yet. You can install the development version of `eurobarometer` from [GitHub](https://github.com/dataobservatory-eu/eurobarometer) with `devtools`.  If you have not used devtools yet, please refer to the [Installation Guide](https://eurobarometer.dataobservatory.eu/articles/installation.html) vignette:

``` r
# install.packages("devtools")
devtools::install_github("dataobservatory-eu/eurobarometer")
```

## Import Surveys

The `read_sav_gesis()` function is a wrapper with `DDIwR::convert()` with the following modifications:

```{r read-file}
library(eurobarometer)
ZA5933 <- read_sav_gesis(file = system.file("extdata", "ZA5933_sample.sav", 
                                            package = "eurobarometer"))
```

## Work with Codebooks

```{r}
codebook_create(ZA5933[, c("d25", "d60")], 
                val_labels = TRUE, 
                freq = TRUE)
```

For further details, see [Codebooks with retroharmonize](https://eurobarometer.dataobservatory.eu/articles/codebook.html) and 
[Eurobarometer Question Bank & Basic Code Table](https://eurobarometer.dataobservatory.eu/articles/questionbank.html) vignettes.

## Harmonization with Crosswalk Tables

For further details, see [Harmonize Surveys with Crosswalk Tables](https://eurobarometer.dataobservatory.eu/articles/crosswalk.html) vignette.


## Archivation

For further details, see [DDI Codebooks with DDIwR](https://eurobarometer.dataobservatory.eu/articles/DDIwR.html) vignette.

## Reviewability & Unit Testing

The human peer-review of output from many surveys is very difficult due to the high dimensionality of the harmonized survey datasets. We would like to support review with several forms of unit testing and automation.  See [Reviewability & Unit Testing](https://eurobarometer.dataobservatory.eu/articles/testing.html) for further details.

## Under the Hood

For further details, see [Dependencies: Other R packages Used](https://eurobarometer.dataobservatory.eu/articles/dependencies.html) vignette.
