---
title: "Codebook"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Codebook}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r settings, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eurobarometer)
```

```{r create-codebook-vignette-dir}
codebook_vignette_dir <- file.path(tempdir(), "codebook_vignette")
if(!dir.exists(codebook_vignette_dir)) {
  dir.create(codebook_vignette_dir)
}
```
This code created the _`r codebook_vignette_dir`_ directory.  You can replicate this vignette with the code above, or you can use your own directory for trying the `codebook_create()` function.

The 'eurobarometer' R packagage contains two, very small subsamples of Eurobarometer microdata file. You cannot work in the `system.file()` of the package, so we will copy the contents of this directory to the temporary folder.

```{r check-sytem-fiiles}
sample_files <- dir(system.file("extdata", package = "eurobarometer"))
sample_files
```
```{r copy-sample-files}
sytem_file_paths <- file.path(
  system.file("extdata", package = "eurobarometer"), 
  dir(system.file("extdata", package = "eurobarometer"))
  )

for (i in seq_along(sample_files)) {
  file.copy(sytem_file_paths[i], file.path(codebook_vignette_dir, sample_files[i]), 
            overwrite=TRUE)
}
```

The resulting files can be found here:

```{r show-sample-files}
sample_files <- file.path(codebook_vignette_dir, dir(codebook_vignette_dir))
sample_files
```
## Create A Survey Codebook

Let's start with `ZA5933_sample.sav`, because it is a better labelled source file.

```{r read-sav-gesis}
sample_data <- read_sav_gesis(
  file = sample_files[2])
```

Let's see the files contents:

```{r simplified-code-table}
simple_codebook <- codebook_create(sample_data, val_labels = FALSE, freq = FALSE)
simple_codebook
```
The simplified codebook is returned in a `dataset`, an s3 class of [dataset](https://dataset.dataobservatory.eu/) package that adds important structural and referencial metadata to an R data.frame. 

The `get_zacat_data_url(simple_codebook$ZACAT[1])` command will return the URL of the 
original dataset, [https://search.gesis.org/research_data/ZA5933](https://search.gesis.org/research_data/ZA5933).

The entire codebook of the sample file would be very large to show, so we subset the `sample_data` and create a more detailed codebook for only the `d25` and `d60` variables.

```{r codebook}
full_codebook <- codebook_create(sample_data[, c("d25", "d60")], 
                                 val_labels = TRUE, 
                                 freq = TRUE)
full_codebook
```

```{r subset-for-d25}
full_codebook[full_codebook$var_name_orig=="d25", c("val_label_orig")]
```


## Work with Multiple Surveys

```{r codebooks}
# Create the joint codebook for multiple files
joint_codebook <- codebook_create(directory = codebook_vignette_dir, 
                                  val_labels = FALSE, 
                                  freq = FALSE)

# Create a random row selection
set.seed(2022)
random_rows <- c(1, sort(round(runif(11, 2, nrow(joint_codebook)),0)))

# Print only the 12 rows 
joint_codebook[random_rows, ]

```
