---
title: "DDI Codebooks with DDIwR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DDI Codebooks with DDIwR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r libraries, message=FALSE}
library(eurobarometer)
library(here)
library(dplyr)
```


The `read_sav_gesis()` function is a wrapper with [haven::read_sav](https://haven.tidyverse.org/reference/read_spss.html),  `declared:as.declared`, and [dataset::dublincore_add](https://dataset.dataobservatory.eu/reference/dublincore.html).


```{r read-example-file}
ZA5933 <- read_sav_gesis(file = system.file("extdata", "ZA5933_sample.sav", 
                                            package = "eurobarometer"))
```

The `read_sav_gesis` read in the file into `declared` class.

```{r}
demography_vars <- get_demography_schema() 
```

Let us convert any variables where labelling plays no role to a simpler class. In this case, we will convert the `id` variable to a character vector, and the `d11` (AGE EXACT) variable into a numeric.

```{r}
demography <-ZA5933 %>%
  select( any_of( demography_vars$var_name_orig )) %>%
  mutate ( ## convert to numeric with keeping var_label
    across
    (demography_vars$var_name_orig[which(demography_vars$class_target == "numeric")], as_numeric)
  ) %>%
  mutate ( ## convert to character with keeping var_label
    across
    (demography_vars$var_name_orig[which(demography_vars$class_target == "character")], as.character)
  ) %>%
  mutate ( ## do the same with targeted factor variables (none in this example) 
    across
    (demography_vars$var_name_orig[which(demography_vars$class_target == "factor")], as.factor)
  ) 
```

It is unclear to me what happens here. Neither the documentation specifies the outcome, nor I do not see anything happening.

```{r}
library(DDIwR)
DDI_demograpy <- convert(demography, to = "DDI", embed=TRUE)
print(DDI_demograpy)
```


```{r, results='asis', message=FALSE}
library(knitr)
library(kableExtra)
var_code_table(df = demography, var_name = "d7") %>%
  #mutate (var_name_orig = cell_spec(.data$var_name_orig, align="c")) %>%
  kbl( align = c(rep("c",4), "l")) %>%
  kable_paper(full_width = F, font_size = 10) %>%
  add_header_above(c("id" = 1, "variable properies" = 2, "value properties" = 2)) %>%
  column_spec(1, bold = F, border_right = T, width = "2.5em") %>%
  column_spec(2:4, bold = F, width = "2.5em")  %>%
  column_spec(3, border_right = T)  %>%
  column_spec(5, border_right=T)
```
