---
title: "Dependencies: Other R packages Used"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dependencies: Other R packages Used}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eurobarometer)
```

The `read_sav_gesis()` function is a wrapper with `DDIwR::convert()` with the following modifications:

```{r read-file}
ZA5933 <- read_sav_gesis(file = system.file("extdata", "ZA5933_sample.sav", 
                                            package = "eurobarometer"))
```

- The original, labelled survey variables are stored as [declared](https://declared.dataobservatory.eu/reference/declared.html), which has many advantages compared to the labelled class used by haven.
- The study-level metadata is added as metadata to the data.frame with [dataset::dublincore_add](https://dataset.dataobservatory.eu/reference/dublincore.html).
- A truly unique identifier is added to the dataset. GESIS's `uniqid` identifier is designed to be unique within one _wave_ of Eurobarometer surveys.  To avoid identification duplication, retroharmonize adds an `id` to each row.

```{r small-sample, echo=FALSE, message=FALSE}
library(dplyr)
set.seed(1234)
ZA5933_sample <-ZA5933 %>%
  select ( any_of(c("id", "uniqid", "d25"))) %>%
  sample_n(12) %>%
  mutate ( d25_num = as.numeric(.data$d25), 
           d25_chr = as.character(.data$d25))
```

## Advantages of declared

The use of declared makes type conversions (and recoding, relabelling) easier.

```{r declared-class}
ZA5933_sample$d25_num
ZA5933_sample$d25_chr
```

## Advantages of dataset

The use of `dataset` helps to retain dataset-level metadata, which is critically important when we will combine datasets of different Eurobarometer survey waves, or make other interventions in the various stages of the survey lifecycle.

```{r dataset-metadata}
library(dataset)
ZA5933_sample
```



```{r attributes}
attributes(ZA5933_sample)
```
