---
title: "Installation Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Because `eurobarometer` is in an early development phase, you cannot install it from CRAN with the `install.packages("eurobarometer")` command yet. You can install the development version of `eurobarometer` from [GitHub](https://github.com/dataobservatory-eu/eurobarometer) with `devtools`. 

For installing a not-yet-released package, you not only need R to be installed on your computer, but must be able to build packages from source (those that need compilation of C/C++ or Fortran code).  

- On Ubuntu, you need to install _r-base-dev_ with `sudo apt-get install r-base-dev`, see [further information](https://cran.r-project.org/bin/linux/ubuntu/fullREADME.html).

- On Windows install the latest version of  [Rtools](https://cran.r-project.org/bin/windows/Rtools/).

- On Mac install from Terminal _Xcode_ with `xcode-select --install`.

Once you can work with development version packages, run `install.packages("devtools")`.

If `devools` is correctly installed on your computer, you can install `eurobarometer`:

``` r
devtools::install_github("dataobservatory-eu/eurobarometer")
```

You need to install the dependencies together with their dependencies:

```{r, eval=FALSE}
install.packages(c("dataset", "declared", "retroharmonize", "DDIwR"))
```


To install the latest development version of _DDIwR_ (not needed for this version of _eurobarometer_): 

```{r, eval=FALSE}
devtools::install_github("dusadrian/DDIwR")
```


Back to [README](https://eurobarometer.dataobservatory.eu/).

