---
title: "Eurobarometer Question Bank & Basic Code Table"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Eurobarometer Question Bank}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eurobarometer)
```

We create a minimal question bank and a codebook for the most important variables of the GESIS Eurobarometer microdata files. These are the variables that are likely to be needed in every harmonization job.

```{r}
data("eurobarometer_basic_codebook")
print(eurobarometer_basic_codebook)
```

## Identification

We place the survey-level metadata, such as the title of the survey, the DOI of the survey file, into a dataset metadata. 

The most important variable that needs to be found is the unique case id for every response.  In more recent Eurobarometers, this is always called `uniqid`.  In older files, it needs to be looked up.  The installed version of `eurobarometer` will contain this crucial information.

## Protocol variables

Our basic codebook contains one metadata variable, the date of the interview. In recent Eurobarometer files, this is the `p1` variable. In earlier files, it maybe necessary to look up this file.

## Weight variables

In recent Eurobarometer files, most, but not all weight variables are consistently named. We locate the two important variables, `w1` (basic post-stratification weight) and `wex` (weight extrapolated on population).

## Basic demography variables

We will include in the basic questionbank, codetable, and we will separately release in processed forms the most important socio-demographic variables.

```{r}
get_demography_schema()
```

_A tutorial will follow on how to use them._
